Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-05 doc/PRF2022/PRF_main.tex

In this work, we employ the newly developed JP model using BIEs ~\cite{Fu20, Fu2022_JFM} 
and tune the boundary conditions with energy normalization to study the  collective dynamics of 
amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under various flowing conditions (quiescent flow, linear shear flow, and Taylor-Green flow).
Three quantities are computed to characterize the dynamics of the collective configurations of JPs: Free energy $F$, strain parameter $E$ and 
scalar order parameter $S_2$. In this numerical study we quantify how the collective hydrodynamics of JPs is affected by an external flow. 
Under a given flow, we use the three measures of deformations to quantify the differences in the collective dynamics between the three types of JPs.
These results, summarized below, may provide some general insight into the dynamic control of active particles in a viscous suspension.

@@

Under a relatively weak linear shear flow, the amphiphilic (BC (i)) JPs behave as a unilamellar vesicle that elongates and tank-treads.
For the multi-lamella (BC (ii)) and the striated (BC (iii)) structures  the assembly of JPs behaves like a rigid body with minimal deformation. The effective 
viscosity of the material gives a quantitative validation to support the statement. High 
shear-rate cases provide a range for critical shear rates where the structures break 
apart and undergo major topological changes. 
We further showed that
free energy, scalar order parameter, and strain are effective measures to quantitatively capture the dynamics of the JP oligomers under a linear shear flow.

Under a Taylor-Green flow,  we find that the amphiphilic JPs to be most interesting, exhibiting different vesicle shapes depending on the ratio of the size of the
TG flow to the vesicle size. These results show that we can control the shape of the vesicle to be a square shape or a polygonal shape by adjusting the size of
the cell in TG flow. On the other hand, the assembly of multi-lamella JPs and the striated JPs behaves more or less as a rigid body with connected subdomains, with the number of subdomains increasing with stronger strength of the TG flow.

>>>>

In this work, we employ the newly developed JP model using BIEs ~\cite{Fu20, Fu2022_JFM} 
and tune the boundary conditions with energy normalization to study the  collective dynamics of 
amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under various flowing conditions (quiescent flow, linear shear flow, and Taylor-Green flow).
Three quantities are computed to characterize the dynamics of the collective configurations of JPs: Free energy $F$, strain parameter $E$ and 
scalar order parameter $S_2$. In this numerical study we quantify how the collective hydrodynamics of JPs is affected by an external flow. 
Under a given flow, we use these three measures of deformations to quantify the differences in the collective dynamics between the three types of JPs.
These results, summarized below, may provide some general insight into the dynamic control of active particles in a viscous suspension.

@@

Under a relatively weak linear shear flow, the amphiphilic (BC (i)) JPs behave as a unilamellar vesicle that elongates and tank-treads, with the scalar order 
parameter increasing over time.
For the multi-lamella (BC (ii)) and the striated (BC (iii)) structures  the assembly of JPs behaves like a rigid body with minimal deformation. The effective 
viscosity of the material gives a quantitative validation to support the statement. High 
shear-rate cases provide a range for critical shear rates where the structures break 
apart and undergo major topological changes. 
We further showed that
free energy, scalar order parameter, and strain are effective measures to quantitatively capture the dynamics of the JP oligomers under a linear shear flow.

Under a Taylor-Green flow,  we find that the amphiphilic JPs to be most interesting, exhibiting different vesicle shapes depending on the ratio of the size of the
TG flow to the vesicle size. These results show that we can control the shape of the vesicle to be a square shape or a polygonal shape by adjusting the size of
the cell in TG flow. On the other hand, the assembly of multi-lamella JPs and the striated JPs behaves more or less as a rigid body with connected subdomains, with the number of subdomains increasing with stronger strength of the TG flow. Overall, we found that the multilamellar (BC (ii)) JPs oligomers behave as a shear-thinning fluid, while the striated (BC (iii)) JPs oligomers possess a yield stress.
